Some Title

### 2023-10-14 output/paper/manuscript.tex
Just tried to compile paper.

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{lineno}
\usepackage{rotating}
\usepackage{float}
\usepackage{typearea}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Some Fancy Title},
  pdfauthor={, and },
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Some Fancy Title}
\author{Lorenzo Fabbri\textsuperscript{1,2,*} \and Martine
Vrijheid\textsuperscript{1,2}}
\date{}

@@

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, boxrule=0pt, breakable, enhanced]}{\end{tcolorbox}}\fi

@@

\hypertarget{abstract}{%
\section*{Abstract}\label{abstract}}
\addcontentsline{toc}{section}{Abstract}

@@

\hypertarget{sec-intro}{%
\section{Introduction}\label{sec-intro}}

\hypertarget{sec-background}{%
\subsection{Background and rationale}\label{sec-background}}

@@

\hypertarget{sec-objectives}{%
\subsection{Objectives}\label{sec-objectives}}

@@

\hypertarget{sec-methods}{%
\section{Methods}\label{sec-methods}}

\hypertarget{sec-design}{%
\subsection{Study design}\label{sec-design}}

@@

\hypertarget{sec-setting}{%
\subsection{Setting}\label{sec-setting}}

@@

\hypertarget{sec-participants}{%
\subsection{Participants}\label{sec-participants}}

@@

\hypertarget{sec-vars}{%
\subsection{Variables}\label{sec-vars}}

@@

\hypertarget{sec-confounders}{%
\subsubsection{Confounders}\label{sec-confounders}}

\hypertarget{sec-edcs}{%
\subsubsection{Endocrine disrupting chemicals}\label{sec-edcs}}

\hypertarget{sec-steroids}{%
\subsubsection{Corticosteroids}\label{sec-steroids}}

\hypertarget{sec-neurodevelopment}{%
\subsubsection{Neurodevelopment}\label{sec-neurodevelopment}}

\hypertarget{sec-dat-sources}{%
\subsection{Data sources and measurement}\label{sec-dat-sources}}

@@

\hypertarget{sec-bias}{%
\subsection{Bias}\label{sec-bias}}

@@

\hypertarget{sec-size}{%
\subsection{Study size}\label{sec-size}}

@@

\hypertarget{sec-quant-vars}{%
\subsection{Quantitative variables}\label{sec-quant-vars}}

@@

\hypertarget{sec-stat-methods}{%
\subsection{Statistical methods}\label{sec-stat-methods}}

@@

  \begin{itemize}
  \tightlist
  \item
    Description of outcome model, weighting method, estimand, and
    balance assessment.
  \item
    Description of method used to estimate effects (e.g.,
    g-computation).
  \item
    Description of method used for SE and CI.
  \end{itemize}
\item
  Describe any methods used to examine subgroups and interactions.
\item
  Explain how missing data were addressed.
\item
  Cohort study: explain how loss to follow-up was addressed.
\item
  Cross-sectional study: describe analytical methods taking account of
  sampling strategy.
\item
  Describe any sensitivity analyses.
\item
  When referring to previous publications for methods' details, include
  a brief description of the approach, key assumptions and limitations,
  and any deviation.
\item
  Names and version numbers for the used software packages, including
  non-data arguments if deviating from the default ones.
\end{itemize}

\hypertarget{sec-res}{%
\section{Results}\label{sec-res}}

\hypertarget{sec-res-participants}{%
\subsection{Participants}\label{sec-res-participants}}

@@

\hypertarget{sec-res-pop-desc}{%
\subsection{Descriptive data}\label{sec-res-pop-desc}}

\hypertarget{sec-res-out-desc}{%
\subsection{Outcome data}\label{sec-res-out-desc}}

\hypertarget{sec-res-main}{%
\subsection{Main results}\label{sec-res-main}}

@@

\hypertarget{sec-res-other}{%
\subsection{Other analyses}\label{sec-res-other}}

@@

\hypertarget{sec-discussion}{%
\section{Discussion}\label{sec-discussion}}

\hypertarget{sec-disc-res-key}{%
\subsection{Key results}\label{sec-disc-res-key}}

@@

\hypertarget{sec-limitations}{%
\subsection{Limitations}\label{sec-limitations}}

@@

\hypertarget{sec-interpretation}{%
\subsection{Interpretation}\label{sec-interpretation}}

@@

\hypertarget{sec-general}{%
\subsection{Generalisability}\label{sec-general}}

@@

\hypertarget{funding}{%
\section{Funding}\label{funding}}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

>>>>

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{lineno}
\usepackage{rotating}
\usepackage{float}
\usepackage{typearea}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Some Title},
  pdfauthor={, and },
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Some Title}
\author{Lorenzo Fabbri\textsuperscript{1,2,*} \and Martine
Vrijheid\textsuperscript{1,2}}
\date{}

@@

@@

\section*{Abstract}\label{abstract}
\addcontentsline{toc}{section}{Abstract}

@@

\section{Introduction}\label{sec-intro}

\subsection{Background and rationale}\label{sec-background}

@@

\subsection{Objectives}\label{sec-objectives}

@@

\section{Methods}\label{sec-methods}

\subsection{Study design}\label{sec-design}

@@

\subsection{Setting}\label{sec-setting}

@@

\subsection{Participants}\label{sec-participants}

@@

\subsection{Variables}\label{sec-vars}

@@

\subsubsection{Confounders}\label{sec-confounders}

\subsubsection{Endocrine disrupting chemicals}\label{sec-edcs}

\subsubsection{Corticosteroids}\label{sec-steroids}

\subsubsection{Neurodevelopment}\label{sec-neurodevelopment}

\subsection{Data sources and measurement}\label{sec-dat-sources}

@@

\subsection{Bias}\label{sec-bias}

@@

\subsection{Study size}\label{sec-size}

@@

\subsection{Quantitative variables}\label{sec-quant-vars}

@@

\subsection{Statistical methods}\label{sec-stat-methods}

@@

  \begin{itemize}
  \tightlist
  \item
    Description of outcome model, weighting method, estimand, and
    balance assessment.
  \item
    Description of method used to estimate effects (e.g.,
    g-computation).
  \item
    Description of method used for SE and CI.
  \end{itemize}
\item
  Describe any methods used to examine subgroups and interactions
  (sub-group analysis or moderation analysis or analysis of
  effect-modification).
\item
  Explain how missing data were addressed.
\item
  Cohort study: explain how loss to follow-up was addressed.
\item
  Cross-sectional study: describe analytical methods taking account of
  sampling strategy.
\item
  Describe any sensitivity analyses.
\item
  When referring to previous publications for methods' details, include
  a brief description of the approach, key assumptions and limitations,
  and any deviation.
\item
  Names and version numbers for the used software packages, including
  non-data arguments if deviating from the default ones.
\end{itemize}

\section{Results}\label{sec-res}

\subsection{Participants}\label{sec-res-participants}

@@

\subsection{Descriptive data}\label{sec-res-pop-desc}

\subsection{Outcome data}\label{sec-res-out-desc}

\subsection{Main results}\label{sec-res-main}

@@

\subsection{Other analyses}\label{sec-res-other}

@@

\section{Discussion}\label{sec-discussion}

\subsection{Key results}\label{sec-disc-res-key}

@@

\subsection{Limitations}\label{sec-limitations}

@@

Some limitations:

\begin{itemize}
\tightlist
\item
  Cross-sectional study.
\item
  Chemicals measured in night and morning samples, whereas metabolites
  (the outcome) were measured only in night samples.
\item
  Cortisol measured at night, when should be lowest.
\item
  Change of estimand when trimming weights.
\item
  Model misspecification.
\item
  Mixtures effect.
\item
  Residual confounding.
\item
  Some confounders were not used since large percentage of missing
  values.
\item
  Multiple comparisons.
\end{itemize}

\subsection{Interpretation}\label{sec-interpretation}

@@

\subsection{Generalisability}\label{sec-general}

@@

\section{Funding}\label{funding}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}
